*Prochlorococcus marinus* responses to light and oxygen

### 2024-02-16 Code/Manuscript_O2.Rmd
edits

```{r FtsHtable, table.cap = FtsHtable_cap, echo = FALSE}

FtsHtable_cap <- glue("FtsH protease homologs in *Prochlorococcus marinus* and the model cyanobacterium *Synechocystis* sp. PCC6803. Protein homology determined by multiple sequence alignment with MUSCLE followed by construction of maximum likelihood phylogenetic tree using 1000 bootstrap replicates in MEGAX.",

                       .sep = " ")
FtsHTable <- tibble(Organism = c("Prochlorococcus marinus", "Synechocystis sp. PCC6803", "Function"),
                    FtsH1 = c("FtsH1", "SlrO22", "PSII Repair"),
                    FtsH2 = c("FtsH2", "Slr1604", "PSII Repair"),
                    FtsH3 = c("FtsH3", "Slr1463", "PSI biogenesis"),
                    FtsH4 = c("FtsH4", "Slr1390", "Cell viability")
                    )

>>>>

```{r FtsHtable, echo = FALSE}

FtsHtable_cap <- "FtsH protease homologs in *Prochlorococcus marinus* and the model cyanobacterium *Synechocystis* sp. PCC6803. Protein homology determined by multiple sequence alignment with MUSCLE followed by construction of maximum likelihood phylogenetic tree using 1000 bootstrap replicates in MEGAX."

FtsHTable <- tibble(Organism = c("Prochlorococcus marinus", "Synechocystis sp. PCC6803", "Function"),
                    FtsH1 = c("FtsH1", "SlrO22", "PSII Repair"),
                    FtsH2 = c("FtsH2", "Slr1604", "PSII Repair"),
                    FtsH3 = c("FtsH3", "Slr1463", "PSI biogenesis"),
                    FtsH4 = c("FtsH4", "Slr1390", "Cell viability")
                    )
